### 2013-07-30 paper.tex
lol intro

For a full treatise, we refer the reader to \cite{ref:Humphreys}.

@@

\section{Problem Statement}
\label{sec:probstate}

The motivation for this problem arises from the following definition.
\begin{definition}
	A map is \emph{idempotent} if multiplying it with itself returns the original map.
\end{definition}
Fix an $\ul r$.  If we can find two maps $A$ and $B$ for which $AB$ is the identity, then $(BA)^2=BABA=BA$ will be an idempotent.  This motivates us to construct potential idempotents by taking two light leaves whose top sequences are identical, and composing $A$ upside-down with $B$, in the hope that $AB=1$.

>>>>

For a full treatise on the topic, we refer the reader to \cite{ref:Humphreys}.

@@

\section{Problem Statement}
\label{sec:probstate}
\begin{definition}
	A map is \emph{idempotent} if multiplying it with itself returns the original map.  Two idempotents are orthogonal if their product is zero.
\end{definition}
Fix an expression $\ul r$.  If we can find two maps $A$ and $B$ for which $AB$ is the identity, then $(BA)^2=BABA=BA$ will be an idempotent.  More generally, however, if $AB = c$ for some scalar $c$, then \[ \left( \frac{BA}{c} \right)\left( \frac{BA}{c} \right) = \frac{BABA}{c^2} = \frac{BA}{c} \] is also an idempotent.  In other words, any two maps with nonzero product can be used to construct an idempotent.

However, if we are interested in finding sets of pairwise orthogonal idempotents, then this becomes a linear algebra problem in which we require a matrix of all possible products.  The construction of such a set of idempotents is closely related to the decomposition of these bimodules, which in turn gives information about the Soergel bimodules\footnote{Actually, the Soergel bimodules may be defined as the images of idempotents in the endomorphism rings of the Bott-Samelson bimodules.}.
